\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-09-10 amta.2016/amta2016.tex
move to amta.2016
delete all [h]

~\cite{mfernandez2016boosting} was concerned with multi-core speed but treated the decoding process as a black box within a parallelization framework.

There are a number of phrase-based decoding implementations, many of which implements the extensions to the phrase-based model described above.

The most well known is Moses~\citep{koehn-EtAl:2007:PosterDemo} which implements a number of speed optimizations, including cube-pruning. It is widely used for MT research and commercial use.

@@

This paper not only focuses on faster single-threaded decoding but also on overcoming the shortcomings of existing decoding implementations on multicore servers.

@@

For any phrase-table table of a realistic size, memory and loading time constraints requires us to use a load-on-demand implementation. Moses has several which we can make use of, each with differing performance characteristics. Figure~\ref{fig:moses-phrase-tables-time} shows the decoding speed for the fastest two implementations.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding speed with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\citep{Bogoychev.probing.2016} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation from hereon.

We propose two optimizations. Firstly, the translation rule caching mechanism in Moses saves the most recently used rules. However, this require locking and active management in clearing of old rules. The result is \emph{slower} decoding, Table~\ref{tab:phrase-table-cache}. 
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& No cache	& Caching \\ \hline
Decoding time  	& 2877	& 2540 (-12\%) \\ \hline
\end{tabular}
\end{center}
\caption{Decoding speed (in words / sec with 32 threads) when using phrase-table cache}
\label{tab:phrase-table-cache}
\end{table}

@@

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus~\citep{tiedemann2012parallel} containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All model files were then binarized; the language models were binarized using KenLM~\citep{Heafield-kenlm}, the phrase table using the Probing phrase-table, lexicalized re-ordering model using the compact data structure. These binary formats were chosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex re. model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}

@@

\begin{table}[h]
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& ar-en		& fr-en \\ \hline
\multicolumn{3}{|l|}{For speed testing} \\ \hline
Set name	& \multicolumn{2}{|c|}{Subset of training data} \\
\# sentences  	& 800k 		& 200k \\
\# words 	& 5.8m 		& 5.9m \\ 
Avg words/sent	& 7.3		& 29.7 \\ \hline
\multicolumn{3}{|l|}{For model score testing} \\ \hline
Set name	& OpenSubtitles	& newstest2011 \\
\# sentences  	& 2000 		& 3003 \\
\# words 	& 14,620 	& 86,162 \\ 
Avg words/sent	& 7.3		& 28.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:test-sets}
\end{table}

@@

As can be seen in Table~\ref{tab:optimizing-memory}, over 24\% of the Moses decoder running time is spent on memory management and this increases to 39\% when 32 threads are used, dampening the scalability of the decoder. By contrast, our decoder spends 11\% on memory management and does not significantly increase with more threads.
\begin{table}[h]
\begin{center}
\small
\begin{tabular}{|l|c|c|c|c|} \hline
		& \multicolumn{2}{c|} {Moses}	& \multicolumn{2}{c|} {Our Work} \\ \hline
\# threads	& 1 		& 32	& 1 		& 32  \\ \hline
Memory  	& 24\%		& 39\% 	& 11\%		& 13\% \\
LM 		& 12\%	 	& 2\% 	& 47\%		& 38\% \\ 
Phrase-table	& 9\%	 	& 5\% 	& 2\%		& 4\% \\ 
Lex RO 		& 8\%	 	& 2\% 	& 2\%		& 2\% \\ 
Search 		& 2\%	 	& 0\% 	& 14\%		& 19\% \\ 
Misc/Unknown	& 45\%	 	& 39\% 	& 24\%		& 29\% \\ \hline
\end{tabular}
\end{center}
\caption{Profile of \%age decoding time}
\label{tab:optimizing-memory}
\end{table}

Figure~\ref{fig:mempool} compares the decoding speed for Moses and our decoder, using the same models, parameters and test set. Our decoder is 4.4 times faster with one thread, and 5.0 times faster using all cores. Like Moses, however, performance actually worsens after approximately 15 threads. %, however, the problem is not as pronounced. This gives us a better foundation on which to build further innovations for fast, multi-core decoding.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{mempool.png}} 
\end{tabular}
\caption{Decoding speed of Moses and our decoder, using the same models}
\label{fig:mempool}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{stack-configuration.png}} 
\end{tabular}
\caption{Trade-off between decoding time average model scores for different stack configurations}
\label{fig:stack-configuration}
\end{figure} 
 %, therefore, we shall stick with this Configuration for the remainder of the paper.

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
% 
We verified that the translation quality of our decoder is comparable to that of Moses in Figure~\ref{fig:bleu}, given the same parameters and models. This fits in with our intention of creating a drop-in replacement for the Moses decoder. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality for different pop-limits}
\label{fig:bleu}
\end{figure}

@@

In the first optimization, we create a static translation model cache containing translation rules that translates the most common source phrases. This is constructed during phrase-table training based on the source counts. The cache is then loaded when the decoder is started. It does not require the overhead of managing an active cache but there is still some overhead in using a cache. 
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Cache size	& Decoding Time & Cache Hit \%age	\\ \hline
Before caching	& 229	& N/A	 \\
0		& 239 (+4.4\%)	& 0\% \\
1,000		& 213 (-7.0\%)	& 11\% \\
2,000		& 204 (-10.9\%)	& 13\% \\
4,000		& 205 (-10.5\%)	& 14\% \\
10,000		& 207 (-9.7\%)	& 17\% \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) for varying cache sizes}
\label{tab:cache}
\end{table}
Overall however, using a static cache result in a 10\% decrease in decoding time if the optimum cache size is used, Table~\ref{tab:cache}.

For the second optimization, we disable the compression of the target side of the translation rules. This increase the size of the binary files from 17GB to 23GB but the time saved not needing to decompress the data resulted in a 1.5\% decrease in decoding time with 1 thread and nearly 7\% when the CPUs are saturated, Table~\ref{tab:compression}.
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
\# threads	& Compressed pt & Non-compressed pt \\ \hline
1		& 3052	& 3006 (-1.5\%) \\
5		& 756	& 644 (-14.8\%) \\
10		& 372	& 362 (-2.7\%) \\
15		& 284	& 250 (-12.0\%) \\
20		& 244	& 227 (-7.0\%) \\
25		& 218	& 209 (-4.1\%) \\
30		& 206	& 192 (-6.8\%) \\
35		& 203	& 189 (-6.9\%) \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) for compressed and non-compressed phrase-tables}
\label{tab:compression}
\end{table}

@@

This resulted in a significant decrease in decoding time, especially with high number of cores, Figure~\ref{fig:lex-ro}. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{lex-ro.png}} 
\end{tabular}
\caption{Decoding speed with Compact Lexicalized Re-ordering, and integrated into a model the phrase-table}
\label{fig:lex-ro}
\end{figure} 
Decoding speed increased by 40\% when using one thread but is 5 times faster when using 32 threads. %In fact, the decoding time with the integrated model is similar to that \emph{without} a lexicalized re-ordering model\footnote{Strangely, using lexicalized re-ordering model results in slightly faster decoding than without the model. We double checked with other datasets. We suspect this may be an artefact of the algorithm or data structures, for example, more work is needed to resolve hypothesis recombination.}. Critically for systems with multicores servers, it enables the decoder to continue to scale, making efficient use of all available cores.

@@

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{scalability.png}} 
\end{tabular}
\caption{Comparison of decoding speed of our work and Moses (with \& without the tcmalloc library}
\label{fig:speed}
\end{figure}

@@

Our decoder show no scalability issues when we tested with the same model and tested set on a larger server, Figure~\ref{fig:more-cores}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{more-cores.png}} 
\end{tabular}
\caption{Decoding speed with more cores}
\label{fig:more-cores}
\end{figure}

We verify the results with the French-English phrase-based system and test set. The speed gains are even greater than the Arabic-English test scenario, Figure~\ref{fig:fr-en-speed}. Our decoder is 5.4 times faster than Moses with a single-thread and 14.5 faster when all cores are saturated.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{fr-en-speed.png}} 
\end{tabular}
\caption{Decoding speed for fr-en model}
\label{fig:fr-en-speed}
\end{figure}

It has been suggested that using a larger language model would overpower the improvements in decoding speed. We tested this conjecture by replacing the language model in the ar-en experiment with a 96GB language model. The time to load of language model is significant (394 sec) and was excluded from the translation speed. Results show that our decoder is 7 times faster than Moses and still scales monotonically until all CPUs are saturated, Figure~\ref{fig:large-lm}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{large-lm.png}} 
\end{tabular}
\caption{Decoding speed with a large language model}
\label{fig:large-lm}
\end{figure}

>>>>

~\cite{mfernandez2016boosting} was concerned with multi-core speed but treated decoding as a black box within a parallelization framework.

There are a number of phrase-based decoding implementations, many of which implements the extensions to the phrase-based model described above. The most well known is Moses~\citep{koehn-EtAl:2007:PosterDemo} which implements a number of speed optimizations, including cube-pruning. It is widely used for MT research and commercial use.

@@

This paper not only focuses on faster single-threaded decoding but also on overcoming the shortcomings of existing decoding implementations on multicore servers. We will compare multicore performance the best-of-breed phrase-table described in ~\cite{junczys_tsd_2012b} with our own implementation. We will use the cube-pruning algorithm, however, the standard phrase-based decoding algorithm is also available.

@@

For any phrase-table table of a realistic size, memory and loading time constraints requires us to use a load-on-demand implementation. Moses has several which we can make use of, each with differing performance characteristics. Figure~\ref{fig:moses-phrase-tables-time} shows the decoding speed for the fastest two implementations.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-phrase-table.png}} 
\end{tabular}
\caption{Moses decoding speed with two different phrase-table implementations}
\label{fig:moses-phrase-tables-time}
\end{figure} 
From this, it appears that the Probing phrase-table~\citep{Bogoychev.probing.2016} has the fastest translation rule lookup, especially with large number of cores, therefore, we will concentrate exclusively on this implementation from hereon.

We propose two optimizations. Firstly, the translation rule caching mechanism in Moses saves the most recently used rules. However, this require locking and active management in clearing of old rules. The result is \emph{slower} decoding, Table~\ref{tab:phrase-table-cache}. 
\begin{table}
\small
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& No cache	& Caching \\ \hline
Decoding time  	& 2877	& 2540 (-12\%) \\ \hline
\end{tabular}
\end{center}
\caption{Decoding speed (in words / sec with 32 threads) when using phrase-table cache}
\label{tab:phrase-table-cache}
\end{table}

@@

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus~\citep{tiedemann2012parallel} containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All model files were then binarized; the language models were binarized using KenLM~\citep{Heafield-kenlm}, the phrase table using the Probing phrase-table, lexicalized re-ordering model using the compact data structure. These binary formats were chosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. 
\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex re. model	& 2.3	& 0.6 \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}

@@

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& ar-en		& fr-en \\ \hline
\multicolumn{3}{|l|}{For speed testing} \\ \hline
Set name	& \multicolumn{2}{|c|}{Subset of training data} \\
\# sentences  	& 800k 		& 200k \\
\# words 	& 5.8m 		& 5.9m \\ 
Avg words/sent	& 7.3		& 29.7 \\ \hline
\multicolumn{3}{|l|}{For model score testing} \\ \hline
Set name	& OpenSubtitles	& newstest2011 \\
\# sentences  	& 2000 		& 3003 \\
\# words 	& 14,620 	& 86,162 \\ 
Avg words/sent	& 7.3		& 28.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:test-sets}
\end{table}

@@

As can be seen in Table~\ref{tab:optimizing-memory}, over 24\% of the Moses decoder running time is spent on memory management and this increases to 39\% when 32 threads are used, dampening the scalability of the decoder. By contrast, our decoder spends 11\% on memory management and does not significantly increase with more threads.
\begin{table}
\begin{center}
\small
\begin{tabular}{|l|c|c|c|c|} \hline
		& \multicolumn{2}{c|} {Moses}	& \multicolumn{2}{c|} {Our Work} \\ \hline
\# threads	& 1 		& 32	& 1 		& 32  \\ \hline
Memory  	& 24\%		& 39\% 	& 11\%		& 13\% \\
LM 		& 12\%	 	& 2\% 	& 47\%		& 38\% \\ 
Phrase-table	& 9\%	 	& 5\% 	& 2\%		& 4\% \\ 
Lex RO 		& 8\%	 	& 2\% 	& 2\%		& 2\% \\ 
Search 		& 2\%	 	& 0\% 	& 14\%		& 19\% \\ 
Misc/Unknown	& 45\%	 	& 39\% 	& 24\%		& 29\% \\ \hline
\end{tabular}
\end{center}
\caption{Profile of \%age decoding time}
\label{tab:optimizing-memory}
\end{table}

Figure~\ref{fig:mempool} compares the decoding speed for Moses and our decoder, using the same models, parameters and test set. Our decoder is 4.4 times faster with one thread, and 5.0 times faster using all cores. Like Moses, however, performance actually worsens after approximately 15 threads. %, however, the problem is not as pronounced. This gives us a better foundation on which to build further innovations for fast, multi-core decoding.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{mempool.png}} 
\end{tabular}
\caption{Decoding speed of Moses and our decoder, using the same models}
\label{fig:mempool}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{stack-configuration.png}} 
\end{tabular}
\caption{Trade-off between decoding time average model scores for different stack configurations}
\label{fig:stack-configuration}
\end{figure} 
 %, therefore, we shall stick with this Configuration for the remainder of the paper.

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
% 
We verified that the translation quality of our decoder is comparable to that of Moses in Figure~\ref{fig:bleu}, given the same parameters and models. This fits in with our intention of creating a drop-in replacement for the Moses decoder. 
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality for different pop-limits}
\label{fig:bleu}
\end{figure}

@@

In the first optimization, we create a static translation model cache containing translation rules that translates the most common source phrases. This is constructed during phrase-table training based on the source counts. The cache is then loaded when the decoder is started. It does not require the overhead of managing an active cache but there is still some overhead in using a cache. 
\begin{table}
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
Cache size	& Decoding Time & Cache Hit \%age	\\ \hline
Before caching	& 229	& N/A	 \\
0		& 239 (+4.4\%)	& 0\% \\
1,000		& 213 (-7.0\%)	& 11\% \\
2,000		& 204 (-10.9\%)	& 13\% \\
4,000		& 205 (-10.5\%)	& 14\% \\
10,000		& 207 (-9.7\%)	& 17\% \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) for varying cache sizes}
\label{tab:cache}
\end{table}
Overall however, using a static cache result in a 10\% decrease in decoding time if the optimum cache size is used, Table~\ref{tab:cache}.

For the second optimization, we disable the compression of the target side of the translation rules. This increase the size of the binary files from 17GB to 23GB but the time saved not needing to decompress the data resulted in a 1.5\% decrease in decoding time with 1 thread and nearly 7\% when the CPUs are saturated, Table~\ref{tab:compression}.
\begin{table}
\small
\begin{center}
\begin{tabular}{|r|r|r|} \hline
\# threads	& Compressed pt & Non-compressed pt \\ \hline
1		& 3052	& 3006 (-1.5\%) \\
5		& 756	& 644 (-14.8\%) \\
10		& 372	& 362 (-2.7\%) \\
15		& 284	& 250 (-12.0\%) \\
20		& 244	& 227 (-7.0\%) \\
25		& 218	& 209 (-4.1\%) \\
30		& 206	& 192 (-6.8\%) \\
35		& 203	& 189 (-6.9\%) \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32 threads) for compressed and non-compressed phrase-tables}
\label{tab:compression}
\end{table}

@@

This resulted in a significant decrease in decoding time, especially with high number of cores, Figure~\ref{fig:lex-ro}. 
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{lex-ro.png}} 
\end{tabular}
\caption{Decoding speed with Compact Lexicalized Re-ordering, and integrated into a model the phrase-table}
\label{fig:lex-ro}
\end{figure} 
Decoding speed increased by 40\% when using one thread but is 5 times faster when using 32 threads. %In fact, the decoding time with the integrated model is similar to that \emph{without} a lexicalized re-ordering model\footnote{Strangely, using lexicalized re-ordering model results in slightly faster decoding than without the model. We double checked with other datasets. We suspect this may be an artefact of the algorithm or data structures, for example, more work is needed to resolve hypothesis recombination.}. Critically for systems with multicores servers, it enables the decoder to continue to scale, making efficient use of all available cores.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{scalability.png}} 
\end{tabular}
\caption{Comparison of decoding speed of our work and Moses (with \& without the tcmalloc library}
\label{fig:speed}
\end{figure}

@@

Our decoder show no scalability issues when we tested with the same model and tested set on a larger server, Figure~\ref{fig:more-cores}.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{more-cores.png}} 
\end{tabular}
\caption{Decoding speed with more cores}
\label{fig:more-cores}
\end{figure}

We verify the results with the French-English phrase-based system and test set. The speed gains are even greater than the Arabic-English test scenario, Figure~\ref{fig:fr-en-speed}. Our decoder is 5.4 times faster than Moses with a single-thread and 14.5 faster when all cores are saturated.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{fr-en-speed.png}} 
\end{tabular}
\caption{Decoding speed for fr-en model}
\label{fig:fr-en-speed}
\end{figure}

It has been suggested that using a larger language model would overpower the improvements in decoding speed. We tested this conjecture by replacing the language model in the ar-en experiment with a 96GB language model. The time to load of language model is significant (394 sec) and was excluded from the translation speed. Results show that our decoder is 7 times faster than Moses and still scales monotonically until all CPUs are saturated, Figure~\ref{fig:large-lm}.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{large-lm.png}} 
\end{tabular}
\caption{Decoding speed with a large language model}
\label{fig:large-lm}
\end{figure}
